TCP Congestion Algorithms In Datacenters \\ \vspace{0.3cm} {\large LS Project}

### 2017-12-11 paper/paper.tex
Added BIC algorithm

		- Includes characteristics of the algorithms. To what do the TCP congestion algorithms respond according to literature? And how do they deal with that (If available in literature).

>>>>

		The BIC algorithm controls its windows based on the size of windows \cite{bic-tcp-congestion}. It consists of two components:
		\begin{enumerate}
			\item Binary search increase. This algorithm computes the midpoint between the maximum window size $W_{max}$ and current minimum window size $W_{min}$. If packet loss occurs, $W_{max}$ is set to the midpoint. This process repeats until $W_{max}$ and $W_{min}$ are smaller than the minimum increment $S_{min}$.
			\item Additive increase runs as an addition to the binary search increase. If $W_{max} - midpoint > S_{max}$, the window size is increased by $S_{max}$ until $W_{max} - midpoint < S_{max}$. $S_{max}$ is the preset maximum increment. 
		\end{enumerate}
In case the current window size becomes greater than $W_{max}$ a slow start strategy is performed to determine a new $W_{max}$: $W_{max} + \alpha * S_{min}$, where $\alpha$ is a multiplier. The multiplier is increased by one until $S_{min} * \alpha >= S_{max}$ or when losses occur. In the case of loss a new value for $W_{max}$ will be set.

		The CUBIC algorithm
